### 2015-06-17 narrative/intro.tex
added some outline material and instructions in the introduction

We propose to explore the development of a performance engineering data pipeline that combines extraction of fine grained monitoring data, collation and curation of this data into a usable distributed object store, and in-situ analysis and visualization of the data to enable performance understanding at extreme scale for application developers and scientific users. Additionally we will explore the characterization of end-to-end pipelines for typical scientific workflows to better identify key optimization points and explore both application and system level optimization models for these data-centric tasks. 
The inherent complexity of extreme scale systems, combining heterogeneous processing architectures, deep memory hierarchy and severe power constraints, provides a challenge for performance engineering…%motivation

>>>>

\section*{Introduction}

\begin{itemize}

\item describe data size problems for getting scientific results out
\item describe annotating and differentiating data storage according to both
use and inherent data qualities (e.g., contains desireable features)
\item describe idea of using heavy compression for less interesting areas and less or no compression for more interesting areas.
\item describe inherent errors in scientific calculations
\item describe lossy compression within error bounds
\item describe how incorporating plug-ins for application aware data compression opportunities to aid data storage
\item describe Sirocco's current state and future designs as a solid foundation on which to work
\item describe how these new features can enhance a system like Sirocco to reduce data intensity
\item describe metadata challenges that we will also have to face.

\end{itemize}

every section should include:

Problem and background, one or more solution approaches, and investigation goals/questions.

Technical Areas

1. Application Intentions.\\
2. Metadata Management (middleware and storage system)\\
3. Pluggable infrastructure for data transformation (storage system)\\
4. Intelligent data mapping to storage/memory hierarchies (middleware and storage system)\\
5. Predictable Performance and resolution tradeoffs\\
6. Data re-generation. (middleware & storage)\\
7. Learning Motifs and data re-organization.\\

### 2015-06-17 participant-table.tex
added some outline material and instructions in the introduction

% Generated by bin/config-participant-table on Fri Jan 17 21:40:42 EST 2014
\newlength{\longestpientry}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Hasan Abbasi} (\emph{habbasi@ornl.gov})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Karsten Schwan} (\emph{schwan@cc.gatech.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Allen Malony} (\emph{malony@cs.uoregon.edu})}}}
\begin{tabularx}{\textwidth}{l>{\raggedright\arraybackslash}X}
\emph{Institution} & \makebox[\longestpientry][l]{\emph{Principal Investigator (Email)}} \quad \emph{Additional Senior Personnel}
\\
\textbf{\gatech} & \makebox[\longestpientry][l]{\textbf{Karsten Schwan} (\emph{schwan@cc.gatech.edu})}\hspace*{1em}\\
\textbf{\oregon} & \makebox[\longestpientry][l]{\textbf{Allen Malony} (\emph{malony@cs.uoregon.edu})}\hspace*{1em}\\
\textbf{\ornl} & \makebox[\longestpientry][l]{\textbf{Hasan Abbasi} (\emph{habbasi@ornl.gov})}\hspace*{1em}\
\end{tabularx}

>>>>

% Generated by bin/config-participant-table on Fri Jan 17 21:40:42 EST 2014
\newlength{\longestpientry}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Hasan Abbasi} (\emph{habbasi@ornl.gov})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Mark Ainsworth} (\emph{schwan@cc.gatech.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Matthew Curry} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Scott Klasky} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Qing Liu} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Gerald Lofstead} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Carlos Maltzahn} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Kimmy Mu} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{Manish Parashar} (\emph{malony@cs.uoregon.edu})}}}
\setlength{\longestpientry}{\maxof{\longestpientry}{\widthof{\textbf{H. Lee Ward} (\emph{malony@cs.uoregon.edu})}}}
\begin{tabularx}{\textwidth}{l>{\raggedright\arraybackslash}X}
\emph{Institution} & \makebox[\longestpientry][l]{\emph{Principal Investigator (Email)}} \quad \emph{Additional Senior Personnel}
\\
\textbf{\gatech} & \makebox[\longestpientry][l]{\textbf{Karsten Schwan} (\emph{schwan@cc.gatech.edu})}\hspace*{1em}\\
\textbf{\oregon} & \makebox[\longestpientry][l]{\textbf{Allen Malony} (\emph{malony@cs.uoregon.edu})}\hspace*{1em}\\
\textbf{\ornl} & \makebox[\longestpientry][l]{\textbf{Hasan Abbasi} (\emph{habbasi@ornl.gov})}\hspace*{1em}\
\end{tabularx}
